### 2019-05-23 manuscript/methods.tex
edits to Stat Inference

Parameters for each of the ten models described were estimated using RevBayes \citep{hoehna_2016}.
Code for analyses and key results are available at \url{https://github.com/roszenil/solploidy}.
We used the method of \citet{fitzjohn_2009} to account for incomplete sampling in all analyses by setting the probability of sampling a species at the present to $595/3000$ since the Solanaceae family has approximately 3,000 species as estimated by the Solanaceae Source project \citep{solsource}.
For all models, we assumed that speciation and extinction parameters had log-normal prior distributions with means equal to the expected net diversification rate $(\text{number of taxa} / [2 \times \text{root age}])$ and standard deviation $0.5$.
Priors for parameters defining trait changes were assumed to be gamma distributed with parameters $k=0.5$ and $\theta=1$. 
For each model, a Markov chain Monte Carlo \citep[MCMC;][]{metropolis1953equation,Hastings1970} was run for 96 hours in the high-performance computational cluster at the Minnesota Supercomputing Institute, which allowed for 5,000 generations of burn-in and a minimum of 200,000 generations of MCMC for each of the 10 models. %B: the number of models changes here? R-my mistake! fixed it
Convergence and mixing of each MCMC chain was determined by ensuring the effective sample size of each parameter was over 200.

We report posterior distributions for the model parameters, and also for the compound parameters of net diversification ($\lambda - \mu$) and extinction fraction ($\mu / \lambda$) for each state.
Additionally, ancestral states at each node in the phylogeny were sampled jointly during the MCMC analyses.
Ancestral state reconstructions for all models can be found in the Supplementary Information and show the maximum posterior estimates of the marginal probability distributions for each of the 594 internal nodes for each of the 10 models. % TODO: add fig refs (or remove the mention of them)
%B: there was an error in the above sentence: no estimates or values after a posteriori (also "posterior" is ok?)

@@

We calculated the marginal likelihood for each of the ten models in RevBayes \citep{hoehna_2016}.
Marginal likelihoods were calculated using 50 stepping stone steps under the methodology of \citet{xie_2010}.
Each stepping stone step was found by calculating 500 generations of burn-in followed by a total of 1,000 MCMC steps (\cref{table:marginallike}).
The calculation of each marginal likelihood ran for 24 hours on a high-performance computational cluster.

Using the marginal likelihood values, we calculated thirteen different Bayes factors.
Six compared the models of ploidy against one other (D/P and D/P+A/B, each with or without diploidization), one compared the breeding system models (I/C and I/C+A/B), and six compared the models with both traits (ID/CD/CP and ID/CD/CP+A/B, each with or without diploidization) (\cref{table:bayesfactors}).
%
Other comparisons between these models are not valid because the input data are different under the different state space codings (\cref{figure:stateclassifications}).
In mathematical terms, the D/P, I/C, and ID/CD/CP state spaces are not `lumpable' with respect to one another \citep{tarasov_2019}.
% E: I think this short explanation is clear enough, especially with the figure.  I'm not sure whether the hierarchical concept is exactly applicable here.
%R: Boris in the introduction mentions this possible causal relationship would that be equivalent to say hierarchical?
Each model comparison is reported with a Bayes factor on the natural log scale: the comparison between models $M_0$ and $M_1$ is $BF(M_0,\ M_1) = \ln[ P(\mathbf{X} | M_0) - P(\mathbf{X} | M_1)]$.
There is `positive' support for $M_0$ when this value is more than 2, `strong' support when it is more than 6, and `very strong' support when it is more than 10 \citep{kass1995}.

>>>>

Parameters for each of the ten models were estimated using RevBayes \citep{hoehna_2016}.
Code for analyses and key results are available as Supplementary Information. % FIXME more permanent than \url{https://github.com/roszenil/solploidy}.
We accounted for incomplete sampling in all analyses by setting the probability of sampling a species at the present to $595/3000$ \citep[using the method of][]{fitzjohn_2009} since the Solanaceae family has approximately 3,000 species \citep{solsource}.
For all models, we assumed that speciation and extinction parameters had log-normal prior distributions with means equal to the expected net diversification rate $(\text{number of taxa} / [2 \times \text{root age}])$ and standard deviation $0.5$.
Priors for parameters defining trait changes were assumed to be gamma distributed with parameters $k=0.5$ and $\theta=1$. 
For each model, a Markov chain Monte Carlo \citep[MCMC;][]{metropolis1953equation,Hastings1970} was run for 96 hours in the high-performance computational cluster at the Minnesota Supercomputing Institute, which allowed for 5,000 generations of burn-in and a minimum of 200,000 generations of MCMC for each of the 10 models. % FIXME see referee comment about reporting convergence, not runtime
Convergence and mixing of each MCMC chain was determined by ensuring the effective sample size of each parameter was over 200.

We report posterior distributions for the model parameters, and also for the compound parameters of net diversification ($\lambda - \mu$) and extinction fraction ($\mu / \lambda$) for each state.
Additionally, ancestral states at each node in the phylogeny were sampled jointly during the MCMC analyses.
Ancestral state reconstructions for all models show the maximum \emph{a posteriori} estimates of the marginal probability distributions for each of the 594 internal nodes for each of the 10 models (\cref{suppfigure:DPnodipasr,suppfigure:DPasr,suppfigure:DPnodipABasr,suppfigure:DPABasr,suppfigure:ICasr,suppfigure:ICABasr,suppfigure:IDCDCPnodipasr,suppfigure:IDCDCPasr,suppfigure:IDCDCPnodipABasr,suppfigure:IDCDCPABasr}). % FIXME: I'm confused about if these are joint or marginal?  A bit more explanation would help.

@@

We calculated the marginal likelihood for each of the ten models using fifty stepping stone steps under the methodology of \citet{xie_2010}, implemented in RevBayes \citep{hoehna_2016}.
Each stepping stone step was found by calculating 500 generations of burn-in followed by a total of 1,000 MCMC steps (\cref{table:marginallike}).
The calculation of each marginal likelihood ran for 24 hours on a high-performance computational cluster. % FIXME: remove?

Using the marginal likelihood values, we calculated thirteen different Bayes factors.
Six compared the models of ploidy against one other ($D/P$ and $D/P+A/B$, each with or without diploidization), one compared the breeding system models ($I/C$ and $I/C+A/B$), and six compared the models with both traits ($ID/CD/CP$ and $ID/CD/CP+A/B$, each with or without diploidization) (\cref{table:bayesfactors}).
%
Other comparisons between these models are not valid because the input data are different under the different state space codings (\cref{figure:stateclassifications}).
In mathematical terms, the $D/P$, $I/C$, and $ID/CD/CP$ state spaces are not `lumpable' with respect to one another \citep{tarasov_2019}. % E: I'm honestly still confused about whether this is true.  From ID/CD/CP, we can lump ID/CD to get D/P, and we can lump CD/CP to get I/C.  FIXME
Each model comparison is reported with a Bayes factor on the natural log scale: the comparison between models $M_0$ and $M_1$ is $BF(M_0,\ M_1) = \ln[ P(\mathbf{X} | M_0) - P(\mathbf{X} | M_1)]$.
There is `positive' support for $M_0$ when this value is more than 2, `strong' support when it is more than 6, and `very strong' support when it is more than 10 \citep{kass1995}.
